\bf An Unitary RG-based Auxiliary Model Approach\\ to Strongly-Correlated Systems

### 2023-02-17 notes/notes.tex
added k-space proof

@@

\section{Nature of the wavefunctions}
In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\). To satisfy Bloch's theorem means to behave in acertain way under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
\begin{equation}\begin{aligned}
T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
\end{aligned}\end{equation}
At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\). Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\). An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\). These translation operators share eigenstates with the momentum operator:
\begin{equation}\begin{aligned}
	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
\end{aligned}\end{equation}
In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}} = \ket{\Psi^{n=0}_{\vec k=\vec k_0}} = \frac{1}{\lambda_{\ket{\vec k_0}} w N}\sum_{\vec R, \vec a}\ket{\psi_\text{aux}\left( \vec R, \vec a \right)}\) of the bulk Hamiltonian. Note that \(\vec k_0\) is simply the Bloch momentum of the ground state.
To obtain Greens functions, we start by calculating real-space matrix elements of the bulk and auxiliary Hamiltonians. The states that we will consider are local excitations on top of the ground state: \(\ket{i} \equiv c^\dagger_{i\sigma}\ket{\Psi_\text{gs} }\). \(i\) represents a lattice site. Sandwiching eq.~\ref{siam_to_hubb} between \(\ket{i}\) and \(\bra{i}\), we get
	\label{diag_mat_ele_1}
	\braket{i | H_\text{H-H} | i} = \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}\sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime}} e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)} \braket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right) | c_{i\sigma} \mathcal{H}_\text{aux}\left( \vec R_j \right) c^\dagger_{i\sigma}  | \psi_\text{aux}\left( \vec R_m, \vec a \right)}
There are, in general, three auxiliary models in the final expression on the right hand side - one at \(\vec R_n\), one at \(\vec R_m\) and another at \(\vec R_j\). In order to rewrite everything in terms of a single auxiliary model at the origin \(\vec R_0\) of the lattice, we will use the translation operators:
	\ket{\psi_\text{aux}\left( \vec R_m, \vec a \right)} = T\left(\vec R_0 - \vec R_m\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a\right)}, ~ \ket{\psi_\text{aux}\left( \vec R_n, \vec a^\prime \right)} = T\left(\vec R_0 - \vec R_n\right) \ket{\psi_\text{aux}\left(\vec R_0, \vec a^\prime\right)}\\
	\mathcal{H}_\text{aux}\left( \vec R_j \right) = T\left(\vec R_0 - \vec R_j\right) \mathcal{H}_\text{aux}\left( \vec R_0 \right) T^\dagger\left(\vec R_0 - \vec R_j\right)
Substituting these forms into the expression in eq.~\ref{diag_mat_ele_1} gives
	&\braket{i | H_\text{H-H} | i} =\\
	&\sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\mathcal{H}_\text{aux}\left( \vec R_0 \right)T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma}  T\left( \vec R_0 - \vec R_m \right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
We will now absorb some of the translation operators into the creation and annihilation operators \(c_{i\sigma}\) that describe the excitation:
	T^\dagger\left( \vec R_0 - \vec R_n \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right) &= T^\dagger\left( \vec R_0 - \vec R_n \right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right) \\
												    &= T^\dagger\left( \vec R_0 - \vec R_n \right) T^\dagger \left(\vec R_j - \vec R_0\right) T\left(\vec R_j - \vec R_0\right) c_{\sigma}\left( \vec R_i \right)  T^\dagger\left(\vec R_j - \vec R_0\right)\\
												    &=T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}
There, we used \(T^\dagger(\vec R_1) T^\dagger (\vec R_2) = T^\dagger(\vec R_1 + \vec R_2)\). For the creation operator, we similarly get
	T^\dagger\left( \vec R_0 - \vec R_j \right) c^\dagger_{i\sigma} T\left( \vec R_0 - \vec R_m \right) = \left[T^\dagger\left( \vec R_0 - \vec R_m \right) c_{i\sigma} T\left( \vec R_0 - \vec R_j \right)\right]^\dagger = c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)
The operator \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\) creates an electron of spin \(\sigma\) at the position \(\vec R_i - \vec R_j + \vec R_0\). It will be represented as \(c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\). Substituting these forms gives
	&\braket{i | H_\text{H-H} | i} \\
	&= \sum_{\vec R_j, \vec R_m, \atop{\vec R_n, \vec a, \vec a^\prime}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime\right) | T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)| \psi_\text{aux}\left( \vec R_0, \vec a \right)}
To resolve the remaining translation operators, we will now insert the eigenstates \(1 = \sum_{\vec k}\ket{\Psi_{\vec k}}\bra{\Psi_{\vec k}}\) in between the operators.
	\braket{i | H_\text{H-H} | i} = \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{k_0}\cdot\left(\vec{R}_m - \vec R_n\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma} T\left(\vec R_j - \vec R_m\right)\\
	\ket{\Psi_{\vec k_1}}\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}
From Bloch's theorem, we have
T\left(\vec R_j - \vec R_m\right)\ket{\Psi_{\vec k_1}} = e^{i \vec{k}_1\cdot\left(\vec{R}_j - \vec R_m\right)}\ket{\Psi_{\vec k_1}}, ~ ~\bra{\Psi_{\vec k_2}}T^\dagger\left(\vec R_j - \vec R_n\right) = \bra{\Psi_{\vec k_2}}e^{-i \vec{k}_2\cdot\left(\vec{R}_j - \vec R_n\right)}~.
 Substituting this gives
	&\braket{i | H_\text{H-H} | i} =\\
	& \sum_{\vec R_j, \vec R_m, \vec R_n, \atop{\vec a, \vec a^\prime, \vec k_1, \vec k_2}} \frac{e^{i\vec{R}_j\cdot\left(\vec{k}_1 - \vec k_2\right) + i\vec{R}_n\cdot\left(\vec{k}_2 - \vec k\right) + i\vec{R}_m\cdot\left(\vec{k_0} - \vec k_1\right)}}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2}  \braket{\psi_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k_2}}\bra{\Psi_{\vec k_2}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_1}}\\
	&\times\braket{\Psi_{\vec k_1} | \psi_\text{aux}\left( \vec R_0, \vec a \right)}\\
	&= \frac{1}{|\lambda_{\ket{\vec k_0}}|^2 w^2 N^2} \sum_{\vec R_j, \vec a, \vec a^\prime \atop{\vec k_1,\vec k_2}} N^2 \delta_{\vec{k_0},\vec k_2} \delta_{\vec{k_0},\vec k_1} \braket{\psi^0_\text{aux}\left( \vec R_0, \vec a^\prime \right) | \Psi_{\vec k}}\bra{\Psi_{\vec k_0}} c_{\vec R_i - \vec R_j + \vec R_0,\sigma}\mathcal{H}_\text{aux}\left( \vec R_0 \right)c^\dagger_{\vec R_i - \vec R_j + \vec R_0,\sigma}\ket{\Psi_{\vec k_0}}\braket{\Psi_{\vec k_0} | \psi^0_\text{aux}\left( \vec R_0, \vec a \right)}\\

>>>>

\section{Nature of the wavefunctions}
In the tight-binding approach to lattice problems, the full Hamiltonian is described by adding the localised Hamiltonians at each site, and the full wavefunction \(\Psi\) is then obtained by constructing liner combinations of the eigenstates \(\psi_i\) of the local Hamiltonians such that \(\Psi\) satisfies Bloch's theorem: \(\Psi_{\vec k}(\vec r) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r - \vec R_i)\). Bloch's theorem ensures that eigenstates satisfy the following relation under a translation operation \(T(\vec R)\) by some lattice distance \(\vec R = \sum_i n_i \vec a_i\):
\begin{equation}\begin{aligned}
T(\vec R)\Psi_{\vec k}\left(\vec r\right) = \Psi_{\vec k}(\vec r + \vec R) = \sum_i e^{i \vec{k}\cdot\vec{R}_i} \psi_i(\vec r + \vec R - \vec R_i) = e^{i \vec{k}\cdot\vec{R}}\sum_i e^{i \vec{k}\cdot\left(\vec{R}_i - \vec R\right)} \psi_i(\vec r - (\vec R_i - \vec R)) = e^{\vec{k}\cdot\vec{R}}\Psi(\vec r)
\end{aligned}\end{equation}
At the end, we used the fact that \(\vec r_i - \vec R\) is just another lattice vector \(\vec R_j\). Note that the translation operator has been defined as an operation that simply advances the argument of the wavefunction from \(\vec r\) to \(\vec r + \vec R\). An equivalent definition can be given in terms of their action on position eigenkets: \(T(\vec R)\ket{\vec r} = \ket{\vec r - \vec R}\). These translation operators share eigenstates with the momentum operator:
\begin{equation}\begin{aligned}
	T\left( \vec R \right) \ket{\vec k} = \sum_{\vec r_i} e^{i \vec{k}\cdot\vec{r}_i}T\left( \vec R \right)\ket{\vec r_i} = e^{i \vec{k}\cdot\vec{R}}\sum_{\vec r_i} e^{i \vec{k}\cdot\left(\vec{r}_i - \vec R\right)}\ket{\vec r_i - \vec R} = e^{i \vec{k}\cdot\vec{R}} \ket{\vec k}
\end{aligned}\end{equation}
In the previous part, we obtained, among other states, the ground state \(\ket{\Psi_\text{gs}}\) of the bulk Hamiltonian in terms of the ground-states \(\ket{\psi_\text{aux}}\) of the auxiliary models.
In this section, we will relate real-sapce Greens functions of the bulk lattice to those of the auxiliary model. We will assume that the auxiliary model Hilbert space has the same dimensions as that of the bulk lattice model.
We define the time-domain Greens function between two points \(\vec R\) and \(\vec R + \vec r\) as
	G(\vec r, t) = -i\theta(t) \braket{\Psi_\text{gs} | \left\{ c(\vec R + r,t), c^\dagger(\vec R) \right\} | \Psi_\text{gs}}
We also define a Green operator \(\mathcal{G}(\omega)\):
	\mathcal{G}(\omega) = \frac{1}{\omega - (H_\text{H-H} - E_\text{gs})}~,
where \(\omega\) is the frequency scale for the excitations. This operator can be related to the Greens function through the relation (eq.~\eqref{inv_G_func})
\begin{equation}\begin{aligned}\label{greens_func_bulk}
	G(\vec r, \omega) &= \braket{\Psi_\text{gs} | c(\vec R + r) \mathcal{G}(\omega) c^\dagger(\vec R) | \Psi_\text{gs}} - \braket{\Psi_\text{gs} | c^\dagger(\vec R) \mathcal{G}(-\omega) c(\vec R + r) | \Psi_\text{gs}}\\
			  &= \sum_n\left[\braket{\Psi_\text{gs} | c(\vec R + r) \lambda^-_n \frac{\left(H_\text{H-H}\right)^n}{(\omega + E_\text{gs})^{n+1}} c^\dagger(\vec R) | \Psi_\text{gs}} + \braket{\Psi_\text{gs} | c^\dagger(\vec R) \lambda^+_n \frac{\left(H_\text{H-H}\right)^n}{(\omega - E_\text{gs})^{n+1}} c(\vec R + r) | \Psi_\text{gs}}\right]\\
			  &= \sum_n\left[ \frac{\lambda^-_n}{(\omega + E_\text{gs})^{n+1}} \mathcal{U}(\vec r)^{(n)}_> + \frac{\lambda^+_n}{(\omega - E_\text{gs})^{n+1}} \mathcal{U}(\vec r)^{(n)}_<\right]
where we have defined \(\lambda_n^\pm\) using \(1/(1\pm y) = \sum_n \lambda^\pm_n y^n\), and the retarded and advanced propagation matrix elements \(\mathcal{U}(\vec r)^{(n)}_>  = \braket{\Psi_\text{gs} | c(\vec R + r) \left(H_\text{H-H}\right)^n c^\dagger(\vec R) | \Psi_\text{gs}}, \quad \mathcal{U}(\vec r)^{(n)}_<  = \braket{\Psi_\text{gs} | c^\dagger(\vec R) \left(H_\text{H-H}\right)^n c(\vec R + r) | \Psi_\text{gs}}\).
These matrix elements will now be expressed in terms of auxiliary model properties, starting with the retarded one. By combining with eq.~\eqref{siam_to_hubb} and eq.~\eqref{bloch-states}, we get
\begin{equation}\begin{aligned}\label{retarded_matrix_element}
	\mathcal{U}(\vec r)^{(n)}_> = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_i) | c_{\vec R + \vec r, \sigma} \left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n  c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)}~,
where \(\vec k_0\) is the crystal momentum in the ground-state, and \(\ket{\psi}_\text{aux}(\vec R) = \frac{1}{w}\sum_{\vec a}^{\text{NN of }\vec R} \ket{\psi}_\text{aux}(\vec R, \vec a)\). The exponentiated sum can be simplified by inserting the momentum eigenbasis \(\left\{ \ket{\vec k}\bra{\vec k}\right\} \) of the auxiliary model Hilbert space, and shifting all the Hamiltonians \(\mathcal{H}\left( \vec R_c \right)\) to the origin \(\vec R_0\), using translation operators:
	\left[\sum_{\vec R_c}\mathcal{H}\left( \vec R_c \right)\right]^n &= \left[\sum_{\vec R_c,\vec k,\vec k^\prime}T^\dagger_{\vec R_c - \vec R_0}\ket{\vec k}\bra{\vec k}\mathcal{H}(\vec R_0)\ket{\vec k^\prime}\bra{\vec k^\prime}T_{\vec R_c - \vec R_0}\right]^n = \left[\sum_{\vec k,\vec k^\prime}\ket{\vec k}\bra{\vec k^\prime}\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0)\sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}\right]^n\\
									 &= \left[\sum_{\vec k}\ket{\vec k}\bra{\vec k}\mathcal{H}_{\vec k, \vec k}(\vec R_0)\right]^n = \sum_{\vec k}\ket{\vec k}\bra{\vec k}\left(N_\text{aux}\mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~,
where \(N_\text{aux}\) is the number of sites in the auxiliary mode, and we used
	\mathcal{H}(\vec R_c) = T^\dagger_{\vec R_c - \vec R_0}\mathcal{H}(\vec R_0)T_{\vec R_c - \vec R_0}~,\quad \sum_{\vec R_c}e^{i \left( \vec k^\prime - \vec k \right) \cdot \left(\vec R_c - \vec R_0\right)}  = N_\text{aux}\delta_{\vec k, \vec k^\prime}~,
We also defined the Hamiltonian matrix element \(\mathcal{H}_{\vec k, \vec k^\prime}(\vec R_0) = \braket{\vec k | \mathcal{H}(\vec R_0) | \vec k^\prime}\). Substituting this back into eq.~\eqref{retarded_matrix_element} gives
	\mathcal{U}(\vec r)^{(n)}_> = \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec k} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_i) | c_{\vec R + \vec r, \sigma} | \vec k}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n \braket{\vec k | c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)}~,
We shift the ground-states \(\ket{\psi_\text{aux}}\) to \(\vec R_0\) as well, using the translation operators:
	\sum_{\vec R_j}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger | \psi_\text{aux}(\vec R_j)} &= \sum_{\vec R_j}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_0} | \psi_\text{aux}(\vec R_0)} = \sum_{\vec R_j, \vec q}e^{i\vec R_j \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger e^{-i\vec q\cdot(\vec R_j - \vec R_0)} | \vec q}\braket{\vec q | \psi_\text{aux}(\vec R_0)}\\
															    &= N e^{i\vec R_0 \cdot \vec k_0}\braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}\braket{\vec k_0 | \psi_\text{aux}(\vec R_0)}\\
All the position variation is then transferred to the creation and annihilation operators, leading to the simpler form
	\mathcal{U}(\vec r)^{(n)}_> &= \frac{1}{\lambda_{\vec k_0}^2}\sum_{\vec k} \braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}|\braket{\psi_\text{aux}(\vec R_0) | \vec k_0}|^2\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n \\
				    &= \sum_{\vec k} \braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~.
The advanced correlation \(\mathcal{U}(\vec r)^{(n)}_<\) can be obtained similarly:
	\mathcal{U}(\vec r)^{(n)}_< = \sum_{\vec k} \braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}\left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n~.
Substituting this into eq.~\eqref{greens_func_bulk} gives
	G(\vec r, \omega) &= \sum_{\vec k}\left[\frac{\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}}{\omega + E_\text{gs}}\sum_n\frac{\lambda^-_n \left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n}{(\omega + E_\text{gs})^{n}} + \frac{\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}}{\omega - E_\text{gs}}\sum_n \frac{\lambda^+_n \left(N \mathcal{H}_{\vec k, \vec k}(\vec R_0)\right)^n}{(\omega - E_\text{gs})^{n}}\right]\\
	&= \sum_{\vec k}\left[\frac{\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} \braket{\vec k | c_{\vec R, \sigma}^\dagger | \vec k_0}}{\omega + E_\text{gs} - N\mathcal{H}_{\vec k, \vec k}(\vec R_0)} + \frac{\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0}}{\omega - E_\text{gs} + N\mathcal{H}_{\vec k, \vec k}(\vec R_0)}\right]
Because of strong correlations in the model, the ground-state energy \(\varepsilon_\text{gs}\) of the auxiliary model can be approximated as \(\varepsilon_\text{gs} \sim E_\text{egs}/N\). Moreover, the operator matrix elements in the numerator evaluate to simple phase factors:
	&\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k} &= \sum_{\vec q} e^{-i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 | c_{\vec q, \sigma} | \vec k} = \sum_{\vec q} \theta(|\vec q| - |\vec k_F|) e^{-i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 + \vec q | \vec k} \\
	 &&=  \theta(|\vec k - \vec k_0| - |\vec k_F|) e^{-i\left(\vec k - \vec k_0\right) \cdot \left( \vec R + \vec r \right)} \\
	&\braket{\vec k_0 | c^\dagger_{\vec R, \sigma} | \vec k} &= \sum_{\vec q} e^{i\vec q \cdot \vec R} \braket{\vec k_0 | c^\dagger_{\vec q, \sigma} | \vec k} = \sum_{\vec q} \theta(|\vec k_F| - |\vec q|) e^{i\vec q \cdot \left( \vec R + \vec r \right)} \braket{\vec k_0 - \vec q | \vec k} \\
	 &&=  \theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{i\left(\vec k - \vec k_0\right) \cdot \left( \vec R + \vec r \right)} \\
	 &\braket{\vec k_0 | c_{\vec R + \vec r, \sigma} | \vec k}\braket{\vec k | c^\dagger_{\vec R, \sigma} | \vec k_0} &= \theta(|\vec k - \vec k_0| - |\vec k_F|)e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r},\\
	&\braket{\vec k_0 | c_{\vec R, \sigma}^\dagger | \vec k} \braket{\vec k | c_{\vec R + \vec r, \sigma} | \vec k_0} &= \theta(|\vec k_F| - |\vec k_0 - \vec k|)e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}
With these inputs, we can write down the final form of the Greens function:
	G(\vec r, \Omega) = \sum_{\vec k}\left[\frac{\theta(|\vec k - \vec k_0| - |\vec k_F|) e^{i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{H}_{\vec k, \vec k}} + \frac{\theta(|\vec k_F| - |\vec k_0 - \vec k|) e^{-i\left(\vec k - \vec k_0\right) \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{H}_{\vec k, \vec k}}\right]
In this expression, the state \(\ket{\vec k}\) represents one of total momentum. One can write this in terms of single-particle excitations \(\ket{\vec q},~\vec q = \vec k - \vec k_0\), which is equal to \(c^\dagger_q \ket{\vec k_0}\) when \(q > 0\) and \(c_q \ket{\vec k_0}\) when \(q < 0\). In terms of these single-particle excitations, the Greens function can be written as
	G(\vec r, \Omega) = \sum_{\vec q}\left[\frac{\theta(|\vec q| - |\vec k_F|) e^{i\vec q \cdot \vec r}}{\omega + N\varepsilon_\text{gs} - N\mathcal{E}^p_{\vec q}} + \frac{\theta(|\vec k_F| - |- \vec q|) e^{-i\vec q \cdot \vec r}}{\omega - N\varepsilon_\text{gs} + N\mathcal{E}^h_{\vec q}}\right]~,
where the matrix elements \(\mathcal{E}^p\) and \(\mathcal{E}^h\) for the particle and hole excitations are given by \(\mathcal{E}^p_{\vec q} = \mathcal{H}_{\vec k_0 + \vec q, \vec k_0 + \vec q} = \braket{\vec k_0 | c_{\vec q} \mathcal{H} c^\dagger_{\vec q} | \vec k_0}\) and \(\mathcal{E}^h_{\vec q} = \mathcal{H}_{\vec k_0 - \vec q, \vec k_0 - \vec q} = \braket{\vec k_0 | c^\dagger_{\vec q} \mathcal{H} c_{\vec q} | \vec k_0}\).

By substituting this for all the auxiliary model terms and by using the unitarity condition \(T^\dagger T = 1\), we get
\begin{equation}\begin{aligned}
	\mathcal{U}(\vec r) &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i - \vec R_0} c_{\vec R + \vec r, \sigma} T^\dagger_{\vec R_c - \vec R_0} \mathcal{H}\left(\vec R_0\right) T_{\vec R_c - \vec R_0} c_{\vec R, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_0} | \psi_\text{aux}(\vec R_0)}\\
					     &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i - \vec R_c} c_{\vec R + \vec r + \vec R_0 - \vec R_c, \sigma} \mathcal{H}\left(\vec R_0\right) c_{\vec R + \vec R_0 - \vec R_c, \sigma}^\dagger T^\dagger_{\vec R_j - \vec R_c} | \psi_\text{aux}(\vec R_0)}
\end{aligned}\end{equation}
Since each summation is over all lattice translation vectors, we can make the substitutions \(\vec R_{i(j)} \to \vec R_{i(j)} - \vec R_c\), followed by \(\vec R_c \to \vec R + \vec R_0 - \vec R_c\), to get
\begin{equation}\begin{aligned}
	\mathcal{U}(\vec r) &= \frac{1}{\lambda_{\vec k_0}^2 N^2}\sum_{\vec R_i, \vec R_j, \vec R_c} e^{i\left( \vec R_j - \vec R_i \right) \cdot \vec k_0}\braket{\psi_\text{aux}(\vec R_0) | T_{\vec R_i} c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) c_{\vec R_c, \sigma}^\dagger T^\dagger_{\vec R_j} | \psi_\text{aux}(\vec R_0)}\\
					     &=\frac{1}{\lambda_{\vec k_0}^2}\sum_{\vec R_c} \braket{\psi_\text{aux}(\vec R_0) | \tilde c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) \tilde c_{\vec R_c, \sigma}^\dagger | \psi_\text{aux}(\vec R_0)}
\end{aligned}\end{equation}
where we have defined the modified creation operator 
\begin{equation}\begin{aligned}
	\tilde c^\dagger_{\vec R_c} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec R_j} e^{i \vec R_j \cdot \vec k_0} T^\dagger_{\vec R_j} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec R_j, \vec k} e^{i \vec R_j \cdot \vec k_0} e^{-i \vec R_j \cdot \vec k} \ket{\vec k}\bra{\vec k} = c^\dagger_{\vec R_c} \frac{1}{N}\sum_{\vec k} N \delta_{\vec k,\vec k_0} \ket{\vec k}\bra{\vec k} = c^\dagger_{\vec R_c} \ket{\vec k_0}\bra{\vec k_0}~.
\end{aligned}\end{equation}
\(\ket{\vec k}\) is the many-body eigenstate of the kinetic energy operator, with total momentum \(\vec k\). Because of translation invariance, the matrix element \(\mathcal{C}(\vec R + \vec r, \vec R)\) is independent of the absolute position \(\vec R\) and depends only on the relative distance \(\vec r\). The above relation ensures that in order to calculate the correlation \(\mathcal{C}(\vec r)\) in the bulk Hamiltonian, we need only solve the auxiliary model at \(\vec R_0\) and calculate the matrix elements of the operators \(\tilde c_{\vec R_c + \vec r, \sigma} \mathcal{H}\left(\vec R_0\right) \tilde c_{\vec R_c, \sigma}^\dagger\) in the auxiliary model ground-state.

As discussed above, the local nature of the auxiliary models (onsite matrix element only on the impurity and non-local matrix element only between impurity and zeroth site) renders all diagonal matrix elements zero, except the one for \(i=j\):
\begin{equation}\begin{aligned}
	\braket{i | H_\text{H-H} | i} = \braket{i | \mathcal{H}_\text{aux,i} | i} = \braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \mathcal{H}_\text{aux,i} e^{i \vec{k}\cdot\vec{R}_i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{i\sigma} \mathcal{H}_\text{aux,i} c^\dagger_{i\sigma} | \psi_\text{aux}} = \braket{\psi_\text{aux} | c_{d\sigma} \mathcal{H}_\text{aux} c^\dagger_{d\sigma} | \psi_\text{aux}}
\end{aligned}\end{equation}
At the last step, we recognised \(i\) as the impurity site and rewrote the expression entirely in terms of a site-independent auxiliary model.
Similarly, the off-diagonal matrix element between two nearest-neighbour sites \(i,j\) is obtained as
\begin{equation}\begin{aligned}
	\braket{i | H_\text{H-H} | j} = \braket{i | \left(\mathcal{H}_\text{aux,i} + \mathcal{H}_\text{aux,j}\right) | j} = \frac{1}{w}\braket{\psi_\text{aux} | c_{i\sigma} e^{-i \vec{k}\cdot\vec{R}_i} \left(\mathcal{H}_\text{aux,i,j} + \mathcal{H}_\text{aux,j,i}\right) e^{i \vec{k}\cdot\vec{R}_j} c^\dagger_{j\sigma} | \psi_\text{aux}} \\
	= \frac{1}{w}e^{i \vec{k}\cdot\left(\vec{R}_j - \vec{R}_i\right)}\braket{\psi_\text{aux} | \left(c_{d\sigma}\mathcal{H}_\text{aux} c^\dagger_{0\sigma} + c_{0\sigma}\mathcal{H}_\text{aux} c^\dagger_{d\sigma}\right) | \psi_\text{aux}}
\end{aligned}\end{equation}
\(\mathcal{H}_\text{aux,i,j}\) is the auxiliary model with \(i\) as the impurity site and \(j\) as the bath zeroth site.

@@
